\documentclass[12pt]{article}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{titling}
\usepackage{mathabx}
\usepackage{titlesec}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\author{Tushaar Kamat}
\title{R\'esum\'e}

\pagenumbering{gobble}

\renewcommand{\maketitle}{
  \begin{center}
  \begin{Huge}
    \theauthor
  \end{Huge}

  Email: platypusdiamond@gmail.com

  Phone: (904) 615-0242
  \end{center}
}

\titleformat{\section}
{\LARGE\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{-1em}
{}

\titleformat{\subsubsection}
{\large\bfseries}
{$\Asterisk$}
{.5em}
{}

\begin{document}
\maketitle

\section{Education} 
\subsection{Allen D. Nease High School}
\begin{itemize}
\item Senior at Allen D. Nease High School.
\item 4.74 weighted GPA, 4.0 unweighted. 
\item International Baccalaureate Diploma Candidate
\item Ranked number 2 in class. 
\end{itemize}
\subsection{Exams}
\begin{itemize}
\item National AP Scholar.
\item Ten 5's and one 4 on AP exams.
\item 1570 SAT score (800 on Math section).
\item 35 ACT Score.
\item 6 on IB music exam.
\item National Merit Semifinalist.
\end{itemize}

\section{Extracurricular}
\subsection{Piano}
\begin{itemize}
\item Have learned piano for 10 years, and have experience with both classical
  and Jazz piano.
\item Have played professionally at both a local restaurant and church.
\end{itemize}
\subsection{Tae kwon do}
\begin{itemize}
\item Practiced for 8 years, became a junior instructor. 
\item Earned a first poom black belt.

\end{itemize}
\subsection{Clubs}
\begin{itemize}
\item Equipment manager for Hi-Q.
\item Treasurer for Mu Alpha Theta.
\item Blessings in a Backpack.
\item Robotics Team.
\item National Honor Society. 
\end{itemize}

\subsection{Programming Languages}
Java, Javascript, HTML, CSS, Clojure/Clojurescript, Haskell, Lisp, some C/C++.

\subsection{Markup Languages}
Org mode, Markdown, \LaTeX{}.

\subsection{Technologies}
Android developement, React JS, Linux/UNIX, bash shell, Emacs, vim. 

\section{Service}
\begin{itemize}
\item Volunteer as a cook and server at the Sulzbacher homeless shelter, and am
  part of a group that gives away vegetarian meals to the needy.
\item Participated in Blessings in a Backpack for 3 years.
\item Volunteered at the Cummer Museum for a summer camp.
\item Helped my Tae Kwon Do instructor as an assistant instructor.
\end{itemize}

\section{Accomplishents}
\begin{itemize}
\item Developed \textit{Youwatch}, a mobile application for Android. The
  application lets the user enter certain topics and minimum numbers of views,
  and it scans YouTube for matches.
\item The app has 1000+ users, was featured in an Android news article. 
\end{itemize}

\subsubsection{Web}
\begin{itemize}
\item Developed a small web application for a school project that uses genetic
  algorithms to solve a maze.  
\item The website was developed using React JS, using a compiles-to-javascript
  language (clojurescript). 
\end{itemize}

\subsection{Other}
\begin{itemize}
\item 1st place team in the Project Green District Competition, where our team
  designed and built a piezoelectric tile.
\item Placed in a statewide math competition (MathCounts).
\end{itemize}



\end{document}
