\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[top=.25in]{geometry}
\usepackage{microtype}

\title{Tushaar Kamat \vspace{-1em}}
\author{\normalfont \normalsize tkamat3@gatech.edu\vspace{-.5em}\\ \normalfont \normalsize Georgia Institue of Technology}
\date{}
\begin{document}
\maketitle
\vspace{-1.5em}
\noindent \today\\
\\
George P. Burdell\\
Software Engineering Department\\
White and Gold\\
801 Atlantic Drive\\ 
Atlanta, GA 30332\\
\\
Dear Mr. Burdell\\
\\
\noindent I am writing to you to express interest in a summer internship
position as a Software Developer at White and Gold. I am a Computer Science
Major at the Georgia Institute of Technology, and considering my previous
experience and relevant skills, I believe I am an excellent fit for the role.

\noindent I am already familiar with many different programming languages and
technologies, including Java, Javascript, Android, React JS, and C/C++.
Furthermore, I have previous experience in the field of Software development
through an internship I completed in the summer of 2018, where I worked on the
company's android payment application, along with editing its Wordpress site.

\noindent In addition to my experiences and skills, I have created two functioning
software projects. My Android app, called \textit{Youwatch}, has over 5,000
downloads along with a 4.7 star rating on the Google Play Store, demonstrating
my ability to develop complex, high-quality software that can be used in the
real-world. I have also developed a complex evolution simulator that is
platformed on a Single Page Application online, which demonstrates my abilities
in Web Developement.

\noindent I am drawn to White and Gold because of their presence on the forefront of
advances in Software and Big Data, which matches my natural curiosity and thirst
for knowledge. Because of my previously mentioned skills, along with my passion
for development and technology, I am confident that I will be the best candidate
for this opportunity.

I have enclosed my resume, which further details my education, skills, and
experiences. I look forward with the opportunity to talk with you further.
Please reach me by email at tkamat3@gatech.edu, or call me at (904) 615-0242.
Thank you for your time, and I look forward to hearing from you soon.
\\
\\
Sincerely,
\\
\\
Tushaar Kamat


\end{document}
